---
title: Use of sampler function
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use of sampler function}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install R Package from GitHub
```{r, eval = FALSE}
library(devtools)
install_github("maryclare/sspcomp")
library(sspcomp)
library(Matrix)
```

# Simulate Data for Example

```{r, eval = FALSE}
set.seed(39210)
# We're going to a simulate a response that corresponds to a 10x2 matrix
# with dependence along the second dimension
n <- 10
m <- 2
# We'll have a 5 x 3 array of covariates, with corresponding coefficients having
# AR-1 dependence along the first dimension and unstructured dependence along 
# the second dimension
p1 <- 5
p2 <- 3
# Simulate covariates
X <- array(rnorm(n*m*p1*p2), c(n*m, p1, p2))
# Simulate response dependence covariance matrix
Sigma <- rWishart(n = 1, df = m, Sigma = diag(m))[, , 1]
# Construct coviarance matrix of regression coefficents along first dimension
Omega1 <- make.ar.mat(p = p1, rho = 0.5, inv = FALSE)
# Simulate coviarance matrix of regression coefficents along second dimension
Omega2 <- rWishart(n = 1, df = p2, Sigma = diag(p2))[, , 1]
# Simulate regression coefficients
beta <- c(t(chol(Omega1))%*%matrix(rnorm(p1*p2), nrow = p1, ncol = p2)%*%chol(Omega2))
# Simulate response
Y <- matrix(t(apply(X, 1, "c"))%*%beta, nrow = n, ncol = m) +
  matrix(rnorm(n*m), nrow = n, ncol = m)%*%chol(Sigma)
```

# Normal Prior, Unknown Variances

## AR-1 Along First Dimension of Coefficients
```{r, eval = FALSE}
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "sno")
```

## CAR Along First Dimension of Coefficients
```{r, eval = FALSE}
Neighbs <- matrix(0, nrow = p1, ncol = p1)
Neighbs[1, 2] <- Neighbs[2, 1] <- 
  Neighbs[2, 3] <- Neighbs[3, 2] <- 
  Neighbs[3, 4] <- Neighbs[4, 3] <-
  Neighbs[4, 5] <- Neighbs[5, 4] <- 
  Neighbs[1, 5] <- Neighbs[5, 1] <- 1

samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "sno",
                        Neighbs = Neighbs)
mean(unlist(lapply(samples$rhos, function(rho) {
  mean(diag(cov2cor(ei.inv(diag(1, p1, p1) - rho*Neighbs))[-1, -p1]))
})))
```

## Unstructured Along First Dimension of Coefficients
```{r, eval = FALSE}
samples <- sampler(X = array(c(X), c(dim(X)[1], 1, dim(X)[-1])), Y = Y, 
                   num.samp = 100, prior = "sno", 
                   Omega.half = list(matrix(1, 1, 1), NULL, NULL))
matrix(rowMeans(apply(samples$Omegas[[2]], 1, cov2cor)), p1, p1)
```

## Uncorrelated Along Second Dimension of Coefficients
```{r, eval = FALSE}
samples <- sampler(X = array(c(X), c(dim(X)[1:2], 1, dim(X)[3])), Y = Y, 
                   num.samp = 100, prior = "sno", 
                   Omega.half = list(NULL, NULL, diag(1, p2, p2)))
```

# Normal Prior, Known Variance(s)


## Known Noise Variance
```{r, eval = FALSE}
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "sno", Sig.sq = Sigma)
```

## Known Noise Variance and Penalized Coefficient Variances
```{r, eval = FALSE}
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "sno", Sig.sq = Sigma,
                   Omega.half = list(sym.sq.root(Omega1), sym.sq.root(Omega2)))
```

# Other Priors

## SPN 

```{r, eval = FALSE}
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "spn")
```


## SNG 

```{r, eval = FALSE}
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "sng", c = 0.5)
```

## SPB 

```{r, eval = FALSE}
# As seen below, default settings for the posterior mode optimization for
# inverse scales lead to slow performance
samples <- sampler(X = X, Y = Y, num.samp = 5, prior = "spb", c = 0.5)
# Can be made faster by reducing the max. number of iterations of coordinate
# descent for inverse scales
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "spb", c = 0.5,
                   max.iter.r = 100)
# Can be made even faster by making the tolerance for coordinate descent
# for inverse scales bigger
samples <- sampler(X = X, Y = Y, num.samp = 100, prior = "spb", c = 0.5,
                   max.iter.r = 100, eps.r = 10^(-2))
```
